---
output: html_document
---

<style>
    body .main-container {
        max-width: 100%;
        padding: 0;
        margin: 0;
    }
    .legend-bivar {
        padding: 2px;
        font: 10px Arial, Helvetica, sans-serif;
       background: white;
       box-shadow: none;
       border: black;
       border: 2px solid rgba(0,0,0,0.2);
       border-radius: 5px;
       background-clip: padding-box;
    }

    .legend-bivar img{
       margin: 0;
    }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
```

```{r, echo=FALSE, message=F, warning=F, results = 'hide'}
options(java.parameters = "-Xmx4g" )
library(XLConnect)
library(sp)

wb <- loadWorkbook("data/Demographics/DistrictwiseTotalPopulation.xlsx")
populationData <- readWorksheet(wb, sheet = "HospitalCount", header = TRUE)
populationData <- populationData[order(populationData$District),]
populationData[nrow(populationData)+2,] <- NA

districts <- readRDS("data/IndiaAdminUnits/Districts_2011_simplified.rds")
districts <- districts[order(as.numeric(districts$censuscode)),]

districts@data <- cbind(districts@data,  populationData[,])
var1 <- districts@data$Population.PHC
var2 <- districts@data$Area.PHC
info1 <- districts@data$Total.Population
info2 <- districts@data$Area..sqkm
info3 <- districts@data$Number.of..Primary.Health.Centres
mainNames <- districts@data$DISTRICT

```

```{r, echo=FALSE, message=F, warning=F, results = 'hide'}
round_percent <- function(x) { 
  if(!any(is.na(x))) {
    x <- x/sum(x)*100  # Standardize result
    res <- floor(x)    # Find integer bits
    rsum <- sum(res)   # Find out how much we are missing
    if(rsum<100) { 
        # Distribute points based on remainders and a random tie breaker
        o <- order(x%%1, sample(length(x)), decreasing=TRUE) 
        res[o[1:(100-rsum)]] <- res[o[1:(100-rsum)]]+1
    } 
    res 
  }
}

hoverlabels <- lapply(seq(nrow(districts@data)), function(i) {
  if (is.na(info3[i])) {
    return(paste0('<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/>",         mainNames[i])))
  }
  paste0( '<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/>
        <div style='width:95%%'>
        <span style='float:left'>Population:</span>
        <span style='float:right'> %s </span><br/>
        <span style='float:left'>Area (sqkm):</span>
        <span style='float:right'> %s </span><br/>
        <span style='float:left'>PHCs:</span>
        <span style='float:right'> %s </span><br/>
        <span style='float:left'>Population/PHC:</span>
        <span style='float:right'> %s </span><br/>
        <span style='float:left'>Area(sqkm)/PHC:</span>
        <span style='float:right'> %s </span>
        </div>
        </div>",
        mainNames[i],
        format(info1[i], big.mark=","),
        format(info2[i], big.mark=","),
        info3[i],
        var1 [i],
        var2 [i]
      ), '</p>' ) 
})

```

```{r, echo=F, warning=F, message=F}
library(ggmap)
library(raster)
library(leaflet)

mapspaletteVar1 <- colorQuantile(
  palette = c("#EDEDED", "#FF94C0", "#FF2C54"),
  domain = var1,
  probs = seq(0, 1, length.out = 4)
)

mapspaletteVar2 <- colorQuantile(
  palette = c("#EDEDED", "#94C6E7", "#4CB1DF"),
  domain = var2,
  probs = seq(0, 1, length.out = 4)
)

legend_scale <- data.frame(
  legVar1 = c(rep(1, 3), rep(2, 3), rep(3, 3)),
  legVar2 = c(rep(seq(1, 3, 1), 3)),
  color = c("#F1F1F1", "#C3DEEE", "#A1D3EA",
            "#F7DBE7", "#CAC8E3", "#A6BDDF",
            "#F7C1CB", "#CAAEC8", "#A6A3C4")
)

legend <- ggplot() +
  geom_tile(
    data = legend_scale,
    aes(x = legVar1, y = legVar2, fill = color)
  ) +
  scale_fill_identity() +
  labs(x = "Low \U2192 High\nPopulation/PHC ",
       y = "Area(sqkm)/PHC\nLow \U2192 High") +
  theme(
    axis.title = element_text(size = 20),
    axis.line = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(10, 10, 10, 10),
    plot.background = element_rect(fill = "transparent", color = NA)
  )

# # save SVG legend
ggsave("data/img/districtsPHCslegend.svg", plot = legend,
       width = 3, height = 3, bg = "transparent")
```
## {.tabset}
### India, Districtwise Primary Health Care Centers^[1][2][3]^

<div class = "col-md-8">
<div class = "row">
```{r, echo=FALSE, message=F, warning=F}
library(leaflet.extras)
library(leaflet.minicharts)
library(htmltools)
library(htmlwidgets)
library(legendreverse)

map <- leaflet(width = "100%") %>% 
  addProviderTiles("Esri") %>%
  leafem::addMouseCoordinates() %>% 
  
  addPolygons(data = districts,
              color = "#000000", 
              weight = .50, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.5,
              dashArray = "3",
              fillColor =  ~mapspaletteVar1(var1),
              highlightOptions = highlightOptions(color = "white", weight = 2),
              group = "Population/PHC") %>%
  
  addPolygons(data = districts,
              color = "#000000", 
              weight = .50, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.5,
              dashArray = "3",
              fillColor =  ~mapspaletteVar2(var2),
              label = lapply(hoverlabels, htmltools::HTML),
              highlightOptions = highlightOptions(color = "white", weight = 2),
              group = "Area/PHCs") %>%
  
  addMiniMap(tiles = providers$Esri, toggleDisplay = TRUE) %>% 
  addScaleBar() %>%
  leafem::addMouseCoordinates() %>%
  addSimpleGraticule(showOriginLabel = TRUE) %>%
  addResetMapButton() %>%
  addSearchOSM(options = search) %>%
  addFullscreenControl() %>% 
  
  addControl(
    "<img src = 'data/img/districtsPHCslegend.svg' width = '128' height = '128'>",
    position = "bottomleft",
    className = "legend-bivar"
  ) %>%

htmlwidgets::onRender("
    function(el, x) {
      var myMap = this;
      myMap.on('baselayerchange',
        function (e) {
          e.layer.bringToBack();
          document.getElementById('countryInfo').innerHTML = lookupCountryInfo(e.name);
        })

      myMap.on('tooltipopen',
        function (e) {
          document.getElementById('districtInfo').innerHTML = e.tooltip._content;
          $('.leaflet-tooltip').css('display','none');
        })

      myMap.on('tooltipclose',
        function (e) {
          document.getElementById('districtInfo').innerHTML = '';
        })
    }")

map

```
<font size='1'>*2011 data and boundaries<br/>
Sources:<br/>
[1] http://www.censusindia.gov.in/2011census/population_enumeration.html <br/>
[2] https://en.wikipedia.org/wiki/List_of_districts_in_India <br/>
[3] https://data.gov.in/catalog/district-wise-availability-health-centres-india-0
</font>
</div>
</div>
<div class = "col-md-3">
<div class = "row"  style = "margin-left: 10px">
<h2><b>India</b></h2>
<div id = "countryInfo"><p><div style='width:95%%'><div style='font-size:12px;width:200px;float:left'><span style='float:left'>Population:</span><span style='float:right'> 1,210,854,977 </span><br/><span style='float:left'>Area (sqkm):</span><span style='float:right'> 3,287,240<sup>[2]</sup> </span><br/><span style='float:left'>Total PHCs:</span><span style='float:right'> 23,790<sup>[3]</sup> </span><br/><span style='float:left'>PHCs /10000:</span><span style='float:right'> 0.2</span><br/><span style='float:left'>PHCs /100sqkm:</span><span style='float:right'> 0.75</span></div></div></p>
</div>
<div id = "districtInfo">
</div>
</div>
</div>

### Plots
```{r, echo=F, message=F, warning=F}
library(pals)
library(classInt)
library(plotly)
cols <- stevens.pinkgreen; nbins <- 3

brksVar1 <- classIntervals(var1, n=nbins, style='quantile')
brksVar2 <- classIntervals(var2, n=nbins, style='quantile')
classVar1 <- findCols(brksVar1)
classVar2 <- findCols(brksVar2)

# convert x,y classes into a joint class x+3(y-1)
districts@data$colorCode <- classVar1 + nbins*(classVar2-1)

bcColors <- c("#e8e8e8","#dfb0d6","#be64ac","#ace4e4","#a5add3","#8c62aa","#5ac8c8","#5698b9","#3b4994") 

# scatterplot of two variates showing bins
plot_ly() %>% add_trace(data=districts@data, x = ~var1, y = ~var2, type="scatter", mode="markers", color = ~colorCode, colors = bcColors, text = ~paste(mainNames, ",",districts@data$State...UT,"\n", "No. of PHCs: ",info3))  %>%
add_lines(x = ~var1, y = brksVar2$brks[2], line = list(color = "grey", width = 0.25, dash = "dot")) %>%
add_lines(x = ~var1, y = brksVar2$brks[3], line = list(color = "grey", width = 0.25, dash = "dot")) %>%
add_lines(x = brksVar1$brks[2], y = ~var2, line = list(color = "grey", width = 0.25, dash = "dot")) %>%
add_lines(x = brksVar1$brks[3], y = ~var2, line = list(color = "grey", width = 0.25, dash = "dot")) %>%
add_lines(x = 30000, y = ~var2, line = list(color = "blue", width = 0.25, dash = "dot")) %>%
add_lines(x = 20000, y = ~var2, line = list(color = "blue", width = 0.25, dash = "dot")) %>%
add_lines(x = 51000, y = ~var2, line = list(color = "red", width = 0.25, dash = "dot")) %>%
add_lines(x = ~var1, y = 138.18, line = list(color = "red", width = 0.25, dash = "dot")) %>%
layout(margin=list(t = 75), title = "Districtwise Primary Healthcare Centers", xaxis = list(title = "Population per PHC", range = c(0,200000)), yaxis = list(title = "Area (sqkm) per PHC", range = c(0,1400))) %>%
add_annotations(text = c("[a]","[b]","[c]", "[d]", "[India, average]"),  x = c(20000,30000,brksVar1$brks[2],brksVar1$brks[3],51000), y=1, showarrow=FALSE,textangle=-90, valign="top", yref="paper", xanchor="right", yanchor="top") %>%
add_annotations(text = "[India, average]",  x = 1, y=138, showarrow=FALSE,valign="bottom", xref="paper", xanchor="right", yanchor="bottom") %>%
hide_colorbar() %>%  layout(showlegend = FALSE)

```
<font size='1'>
[a] Indian public health standards norm: 1 PHC for 20000 people in hilly areas<sup>[4]</sup><br/>
[b] Indian public health standards norm: 1 PHC for 30000 people in the plains<sup>[4]</sup><br/>
[c] 33rd percentile of people per PHC<br/>
[d] 66th percentile of people per PHC<br/>

*2011 data and boundaries<br/>
Sources:<br/>
[1] http://www.censusindia.gov.in/2011census/population_enumeration.html <br/>
[2] https://en.wikipedia.org/wiki/List_of_districts_in_India <br/>
[3] https://data.gov.in/catalog/district-wise-availability-health-centres-india-0<br/>
[4] http://vikaspedia.in/health/health-directory/rural-health-care-system-in-india
</font>

### Data

```{r}
library(DT)
populationData <- populationData[order(-populationData$Total.Population),]
populationData <- populationData[-c(641,642),-c(7:12)]
col2cnvrt2 <- c(3:15) #because !#$@# columnDefs indexes from 0
datatable(populationData, rownames = FALSE, options = list(pageLength = 100, columnDefs = list(list(className = 'dt-right', targets = col2cnvrt2)))) %>% formatCurrency(c(3:5,8), '', digits = 0)

```

Source: <br/>
[1]http://www.censusindia.gov.in/2011census/population_enumeration.html<br/>
[2]https://data.gov.in/catalog/district-wise-availability-health-centres-india-0

### Info
```{r}
sessionInfo()
```
