---
output: html_document
---

<style>
    body .main-container {
        max-width: 100%;
        padding: 0;
        margin: 0;
    }
</style>
<script>
  function lookupCountryInfo(val) {
    var result = "";

    var lookup = {
      "Population Density (/sqkm)": "<p><div style='width:95%%'><div style='font-size:12px;width:200px;float:left'><span style='float:left'>Population:</span><span style='float:right'> 1,210,854,977 </span><br/><span style='float:left'>Area (sqkm):</span><span style='float:right'> 3,287,240<sup>[2]</sup> </span><br/><span style='float:left'>Population Density:</span><span style='float:right'> 382/sqkm</span></div></div></p>",
      
      "Population Growth %": "<p><div style='width:95%%'><div style='font-size:12px;width:200px;float:left'><span style='float:left'>Population Growth:</span><span style='float:right'> 17.64 %%</span><br/><span style='float:left'>Population:</span><span style='float:right'> 1,210,854,977</span></div></div></p>",
      
      "Literacy Rate %": "<p><div style='width:95%%'><div style='font-size:12px;width:200px;float:left'><span style='float:left'>Literacy Rate:</span><span style='float:right'> 74.04 %</span><br/><span style='float:left'>Population:</span><span style='float:right'> 1,210,854,977</span><br/><span style='float:left'>Non-literate:</span><span style='float:right'> ~314,337,952</span></div></div></p>",
      
      "Gender Ratio": "<p><div style='font-size:12px;width:200px;float:left'><span style='font-size:12px;'>Gender Ratio: 943 f/1000m<br/><div style='width:95%%'><span style='float:left'>Males</span><span style='float:right'>Females</span><br/><span style='color:#2aa1ec;float:left'>52%%</span><span         style='color:#fe6a59;float:right'>48%%</span><br clear='all'/><span style='background:#2aa1ec;width:52%;float:left'>&nbsp;</span><span style='background:#fe6a59;width:48%;float:right'>&nbsp;</span><br clear='all'/><span style='float:left'>Males: </span><span style='float:right'>623,724,248</span><br/><span style='float:left'>Females: </span><span style='float:right'>586,469,174</span><br/><span style='float:left'>Difference: </span><span style='float:right'>37,255,074</span></div></div></p>"
    };
  
    result = lookup[val];
  
    return result;
  }
  
  window.onload = function () {
    document.getElementById("countryInfo").innerHTML = lookupCountryInfo("Population Density (/sqkm)");
    descendents = document.getElementsByClassName('leaflet-control');
    for(var i=0; i<descendents.length; i++) {
      if(descendents[i].className == 'info legend leaflet-control') {
        if (descendents[i].innerHTML.indexOf("Population Density (/sqkm)") != -1) {
          descendents[i].style.display = 'block';
        } else {
          descendents[i].style.display = 'none';
        }
      }
    }
  }
</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r, echo=FALSE, message=F, warning=F, results = 'hide'}
options(java.parameters = "-Xmx4g" )
library(XLConnect)
library(sp)

wb <- loadWorkbook("data/Demographics/DistrictwiseTotalPopulation.xlsx")
populationData <- readWorksheet(wb, sheet = "TotalPopulation", header = TRUE)
populationData <- populationData[-1,]
populationData <- populationData[order(populationData$District),]
populationData[nrow(populationData)+2,] <- NA

districts <- readRDS("data/IndiaAdminUnits/Districts_2011_simplified.rds")
districts <- districts[order(as.numeric(districts$censuscode)),]

districts@data <- cbind(districts@data,  populationData[,])

```

```{r, echo=FALSE, message=F, warning=F, results = 'hide'}
library(leaflet)
library(leaflet.extras)
library(leaflet.minicharts)
library(ggmap)
library(raster)
library(htmltools)
library(htmlwidgets)
library(legendreverse)

round_percent <- function(x) { 
  if(!any(is.na(x))) {
    x <- x/sum(x)*100  # Standardize result
    res <- floor(x)    # Find integer bits
    rsum <- sum(res)   # Find out how much we are missing
    if(rsum<100) { 
        # Distribute points based on remainders and a random tie breaker
        o <- order(x%%1, sample(length(x)), decreasing=TRUE) 
        res[o[1:(100-rsum)]] <- res[o[1:(100-rsum)]]+1
    } 
    res 
  }
}

hoverlabelsPop <- lapply(seq(nrow(districts@data)), function(i) {
  if (is.na(districts@data$Total.Population[i])) {
    return(paste0('<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/>",         districts@data$DISTRICT[i])))
  }
  paste0( '<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/>
        <div style='width:95%%'>
        <span style='float:left'>Population:</span>
        <span style='float:right'> %s </span><br/>
        <span style='float:left'>Area (sqkm):</span>
        <span style='float:right'> %s </span><br/>
        <span style='float:left'>Population Density:</span>
        <span style='float:right'> %s /sqkm</span>
        </div>
        </div>",
        districts@data[i, "DISTRICT"],
        format(districts@data$Total.Population[i], big.mark=","),
        format(districts@data$Area..sqkm[i], big.mark=","),
        round(districts@data$Total.Population[i]/districts@data$Area..sqkm[i],2)
      ), '</p>' ) 
})

hoverlabelsPopG <- lapply(seq(nrow(districts@data)), function(i) {
  if (is.na(districts@data$Total.Population[i])) {
    return(paste0('<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/></div>",         districts@data[i, "DISTRICT"])))
  }
  paste0( '<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/>
        <div style='width:95%%'>
        <span style='float:left'>Population Growth:</span>
        <span style='float:right'> %s %%</span><br/>
        <span style='float:left'>Population:</span>
        <span style='float:right'> %s</span><br/>
        </div>
        </div>",
        districts@data$DISTRICT[i],
        districts@data$Population.Growth..[i],
        format(districts@data$Total.Population[i], big.mark=",")
      ), '</p>' ) 
})

hoverlabelsLit <- lapply(seq(nrow(districts@data)), function(i) {
  if (is.na(districts@data$Literates[i])) {
    return(paste0('<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/>",         districts@data[i, "State...U"])))
  }
  paste0( '<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/>
        <div style='width:95%%'>
        <span style='float:left'>Literacy Rate:</span>
        <span style='float:right'> %s (%%)</span><br/>
        </div>
        </div>",
        districts@data$DISTRICT[i],
        districts@data$Literacy.Rate..[i]
      ), '</p>' ) 
})

hoverlabelsGR <- lapply(seq(nrow(districts@data)), function(i) {
  if (is.na(districts@data$Col5[i]) || is.na(districts@data$Col6[i])) {
    return(paste0('<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/></div>",         districts@data$DISTRICT[i])))
  }
  nums <- round_percent(c(100*districts@data$Col5[i]/districts@data$Total.Population[i],100*districts@data$Col6[i]/districts@data$Total.Population[i]))
  paste0( '<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/>
        Gender Ratio: %s<br/>
        <div style='width:95%%'>
        <span style='float:left'>Males</span>
        <span style='float:right'>Females</span>
        <br/>
        <span style='color:#2aa1ec;float:left'>%s%%</span>
        <span style='color:#fe6a59;float:right'>%s%%</span><br clear='all'/>
        <span style='background:#2aa1ec;width:%s%%;float:left'>&nbsp;</span>
        <span style='background:#fe6a59;width:%s%%;float:right'>&nbsp;</span>
        <span style='float:left'>Males: </span>
        <span style='float:right'>%s</span><br clear='all'/>
        <span style='float:left'>Females: </span>
        <span style='float:right'>%s</span><br/>
        <span style='float:left'>Difference: </span>
        <span style='float:right'>%s</span>
        </div>
        </div>",
        districts@data$DISTRICT[i],
        districts@data$Gender.Ratio[i],
        nums[1], nums[2],
        nums[1], nums[2],
        format(districts@data$Col5[i], big.mark=","), format(districts@data$Col6[i], big.mark=","), format(districts@data$Col5[i] - districts@data$Col6[i], big.mark=",")
      ), '</p>' ) 
})
```
## {.tabset}
### India, Districtwise population (2011 Census)^[1]^

<div class = "col-md-8">
<div class = "row">
```{r, echo=FALSE, warning=F}
YlOrBr <- c('#ffffcc', '#ffeda0', '#fed976', '#feb24c', '#fd8d3c', '#fc4e2a', '#e31a1c', '#bd0026', '#800026')

mapspalettePop  <- colorQuantile(palette = YlOrBr,
  domain = districts@data$Total.Population/districts@data$Area..sqkm., n = 7, right = TRUE)

mapspalettePopG <- colorQuantile(
  palette = YlOrBr,
  domain = districts@data$Population.Growth.., n = 7, right = TRUE
)

mapspaletteLit  <- colorNumeric(
  palette = "Blues",
  domain = districts@data$Literacy.Rate..)

mapspaletteGR <- colorQuantile(
  palette = YlOrBr,
  reverse = T,
  domain = districts@data$Gender.Ratio, n = 7, right = TRUE
)

map <- leaflet(width = "100%") %>% 
  addProviderTiles("Esri") %>%
  leafem::addMouseCoordinates() %>% 
  
  addPolygons(data = districts,
              color = "#000000", 
              weight = 1, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.8,
              dashArray = "3",
              fillColor =  ~mapspalettePop(districts@data$Total.Population/districts@data$Area..sqkm.),
              label = lapply(hoverlabelsPop, htmltools::HTML),
              highlightOptions = highlightOptions(color = "white", weight = 2),
              group = "Population Density (/sqkm)") %>%
  
  addPolygons(data = districts,
              color = "#000000", 
              weight = 1, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.8,
              dashArray = "3",
              fillColor = ~mapspalettePopG(districts@data$Population.Growth..),
              label = lapply(hoverlabelsPopG, htmltools::HTML),
              highlightOptions = highlightOptions(color = "white", weight = 2),
              group = "Population Growth %") %>%
  
  addPolygons(data = districts,
              color = "#000000", 
              weight = 1, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.8,
              dashArray = "3",
              fillColor =  ~mapspaletteLit(districts@data$Literacy.Rate..),
              label = lapply(hoverlabelsLit, htmltools::HTML),
              highlightOptions = highlightOptions(color = "white", weight = 2),
              group = "Literacy Rate %") %>%
  
  addPolygons(data = districts,
              color = "#000000", 
              weight = 1, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.8,
              dashArray = "3",
              fillColor = ~mapspaletteGR(as.numeric(districts@data$Gender.Ratio)),
              label = lapply(hoverlabelsGR, htmltools::HTML),
              highlightOptions = highlightOptions(color = "white", weight = 2),
              group = "Gender Ratio") %>%
  
  addMiniMap(tiles = providers$Esri, toggleDisplay = TRUE) %>% 
  addScaleBar() %>%
  leafem::addMouseCoordinates() %>%
  addSimpleGraticule(showOriginLabel = TRUE) %>%
  addLegend("bottomleft", pal = mapspalettePop, values = districts@data$Total.Population/districts@data$Area..sqkm., title = "Population Density (/sqkm)", opacity = 1, labFormat = function(type, cuts, p) {
  n = length(cuts)
  p = paste0(round(p * 100), '%')
  cuts = paste0(round(cuts[-1],0))}) %>% 
  
  addLegend("bottomleft", pal = mapspalettePopG, values = districts@data$Population.Growth.., title = "Population Growth %", opacity = 1, labFormat = function(type, cuts, p) {
  n = length(cuts)
  p = paste0(round(p * 100), '%')
  cuts = paste0(round(cuts[-1],0))}) %>%
  
  legendreverse("bottomleft", pal = mapspaletteLit, values = districts@data$Literacy.Rate.., title = "Literacy Rate %", opacity = 1, decreasing = T) %>%
  
  legendreverse("bottomleft", pal = mapspaletteGR, values = districts@data$Gender.Ratio, opacity = 1, decreasing = T, title = "Gender Ratio", labFormat = function(type, cuts, p) {
  n = length(cuts)
  p = paste0(round(p * 100), '%')
  cuts = paste0(round(cuts[-1],0))}) %>%

htmlwidgets::onRender("
    function(el, x) {
      var myMap = this;
      myMap.on('baselayerchange',
        function (e) {
          document.getElementById('countryInfo').innerHTML = lookupCountryInfo(e.name);
          descendents = document.getElementsByClassName('leaflet-control')
          for(var i=0; i<descendents.length; i++) {
            if(descendents[i].className == 'info legend leaflet-control') {
              if (descendents[i].innerHTML.indexOf(e.name) != -1) {
                descendents[i].style.display = 'block';
              } else {
                descendents[i].style.display = 'none';
              }
            }
          }
        })

      myMap.on('tooltipopen',
        function (e) {
          document.getElementById('districtInfo').innerHTML = e.tooltip._content;
          $('.leaflet-tooltip').css('display','none');
        })

      myMap.on('tooltipclose',
        function (e) {
          document.getElementById('districtInfo').innerHTML = '';
        })
    }") %>% 
  
  addLayersControl(
    baseGroups = c("Population Density (/sqkm)", "Population Growth %", "Literacy Rate %", "Gender Ratio"),
    options = layersControlOptions(collapsed = FALSE)
  )

css_fix <- "div.info.legend.leaflet-control br {clear: both;}"
  map <- map %>% prependContent(tags$style(type = "text/css", css_fix))  

map

```
<font size='1'>*2011 data and boundaries<br/>
Sources:<br/>
[1] http://www.censusindia.gov.in/2011census/population_enumeration.html <br/>
[2] https://en.wikipedia.org/wiki/List_of_districts_in_India
</font>
</div>
</div>
<div class = "col-md-3">
<div class = "row"  style = "margin-left: 10px">
<h2><b>India</b></h2>
<div id = "countryInfo">
</div>
<div id = "districtInfo">
</div>
</div>
</div>

### Data

```{r}
# library(DT)
# populationData <- populationData[order(populationData$Rank),]
# datatable(populationData, rownames = FALSE)
```

Source: http://www.censusindia.gov.in/2011census/population_enumeration.html

### Info
