---
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
---

<style>
    body .main-container {
        max-width: 100%;
        padding: 0;
        margin: 0;
    }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo=FALSE, message=F, warning=F, results = 'hide'}
library("leaflet")
library("rgdal")
library("ggmap")
library("raster")
```

### What should we map today?

```{r echo=FALSE, warning=F}
map <- leaflet(width = "100%")  %>%  
  addProviderTiles(providers$Stamen.Terrain, options = tileOptions(minZoom=3, maxZoom=8)) %>% 
  addMiniMap(tiles = providers$Esri, toggleDisplay = TRUE) %>% 
  addScaleBar() %>%
  addSimpleGraticule(showOriginLabel = TRUE) %>%
  setView(lng = 82.5, lat = 21, 4)
map
```

##[Home](index.html)
##[States of India](statesofindia.html)
##[Districts of India](districtsofindia.html)
##[Parliament Constituencies of India](parliamentconstituencies.html)
##[India Rail Network](indianrailwaynetwork.html)
##[Airports in India](indianairports.html)
##[Statewise Gender Ratio](indiastatesgenderratio.html)
