---
output:
  html_document
---

<style>
    body .main-container {
        max-width: 100%;
        padding: 0;
        margin: 0;
    }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo=FALSE, message=F, warning=F, results = 'hide'}
library("leaflet")
library("rgdal")
library("ggmap")
library("raster")
```

### What should we map today?

```{r echo=FALSE, warning=F}
map <- leaflet(width = "100%")  %>%
  addProviderTiles(providers$Esri.WorldStreetMap, options = tileOptions(minZoom=2, maxZoom=18), group = "World Street Map by Esri") %>%
  addProviderTiles(providers$Esri.DeLorme, options = tileOptions(minZoom=2, maxZoom=18), group = "DeLorme by Esri") %>%
  addProviderTiles(providers$OpenTopoMap, options = tileOptions(minZoom=2, maxZoom=18), group = "Open Topological Map") %>%
  addProviderTiles(providers$Esri.WorldImagery, options = tileOptions(minZoom=2, maxZoom=18), group = "Sattelite Imagery by Esri") %>%
  addProviderTiles(providers$Stamen.TerrainBackground, options = tileOptions(minZoom=2, maxZoom=14), group = "Terrain by Stamen") %>%
  addProviderTiles(providers$Stamen.TonerLabels, options = tileOptions(minZoom=2, maxZoom=14), group = "Sattelite Imagery by Esri") %>%
  addProviderTiles(providers$Stamen.TonerLabels, options = tileOptions(minZoom=2, maxZoom=14), group = "Toner Labels by Stamen") %>%

  addMiniMap(tiles = providers$Esri, toggleDisplay = TRUE) %>% 
  addScaleBar() %>%
  addSimpleGraticule(showOriginLabel = TRUE) %>% 
  addLayersControl(
    baseGroups = c("World Street Map by Esri", "DeLorme by Esri", "Open Topological Map", "Terrain by Stamen", "Sattelite Imagery by Esri", "Toner Labels by Stamen"),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  setView(lng = 82.5, lat = 21, 4)
map
```

###[Districtwise Population Growth - Neonatal Mortality Rate comparison](districtNMRPopGrowth_2011.html)
###[Districtwise Neonatal Mortality Rate](districtNMR-FM_2011.html)
###[Districtwise Primary Health Care Centers](districthospitals_2011.html)
###[Districtwise Population Growth vs Literacy Rate Comparison](districtpop-lit_2011.html)
###[Districtwise Literacy Information](districtliteracy_2011.html)
###[Districtwise Population Info (2011 Census)](districtpopulation_2011.html)
###[Statewise Population Info (2011 Census)](populationdata.html)
###[Airports in India](indianairports.html)
###[India Rail Network](indianrailwaynetwork.html)
###[Parliament Constituencies of India](parliamentconstituencies.html)
###[Districts of India](districtsofindia.html)
###[States of India](statesofindia.html)
