---
output: html_document
---

<style>
    body .main-container {
        max-width: 100%;
        padding: 0;
        margin: 0;
    }
</style>

<script>
  function lookupCountryInfo(val) {
    var result = "";

    var lookup = {
      "Population Density (/sqkm)": "<p><div style='width:95%%'><div style='font-size:12px;width:200px;float:left'><span style='float:left'>Population:</span><span style='float:right'> 1,210,854,977 </span><br/><span style='float:left'>Area (sqkm):</span><span style='float:right'> 3,287,240<sup>[2]</sup> </span><br/><span style='float:left'>Population Density:</span><span style='float:right'> 382/sqkm</span></div></div></p>",
      
      "Population Growth %": "<p><div style='width:95%%'><div style='font-size:12px;width:200px;float:left'><span style='float:left'>Population Growth:</span><span style='float:right'> 17.64 %%</span><br/><span style='float:left'>Population:</span><span style='float:right'> 1,210,854,977</span></div></div></p>",
      
      "Literacy Rate %": "<p><div style='width:95%%'><div style='font-size:12px;width:200px;float:left'><span style='float:left'>Literacy Rate:</span><span style='float:right'> 74.04 %</span><br/><span style='float:left'>Population:</span><span style='float:right'> 1,210,854,977</span><br/><span style='float:left'>Non-literate:</span><span style='float:right'> ~314,337,952</span></div></div></p>",
      
      "Gender Ratio": "<p><div style='font-size:12px;width:200px;float:left'><span style='font-size:12px;'>Gender Ratio: 943 f/1000m<br/><div style='width:95%%'><span style='float:left'>Males</span><span style='float:right'>Females</span><br/><span style='color:#2aa1ec;float:left'>52%%</span><span         style='color:#fe6a59;float:right'>48%%</span><br clear='all'/><span style='background:#2aa1ec;width:52%;float:left'>&nbsp;</span><span style='background:#fe6a59;width:48%;float:right'>&nbsp;</span><br clear='all'/><span style='float:left'>Males: </span><span style='float:right'>623,724,248</span><br/><span style='float:left'>Females: </span><span style='float:right'>586,469,174</span><br/><span style='float:left'>Difference: </span><span style='float:right'>37,255,074</span></div></div></p>",
      
      "Urban:Rural": "<p><div style='font-size:12px;width:200px;float:left'><span style='font-size:12px;'>Urban:Rural Ratio: 0.45<br/><div style='width:95%%'><span style='float:left'>Urban</span><span style='float:right'>Rural</span><br/><span style='color:#2aa1ec;float:left'>31%%</span><span style='color:#fe6a59;float:right'>69%%</span><br clear='all'/><span style='background:#2aa1ec;width:31%;float:left'>&nbsp;</span><span style='background:#fe6a59;width:69%;float:right'>&nbsp;</span><br clear='all'/><span style='float:left'>Urban Population: </span><span style='float:right'>377,105,760</span><br/><span style='float:left'>Rural Population: </span><span style='float:right'>833,087,662</span><br/><span style='float:left'>Total Population: </span><span style='float:right'>1,210,854,977</span></div></div></p>"
    };
  
    result = lookup[val];
  
    return result;
  }

  window.onload = function () {
    document.getElementById("countryInfo").innerHTML = lookupCountryInfo("Population Density");
    descendents = document.getElementsByClassName('leaflet-control');
    for(var i=0; i<descendents.length; i++) {
      if(descendents[i].className == 'info legend leaflet-control') {
        if (descendents[i].innerHTML.indexOf("Population Density") != -1) {
          descendents[i].style.display = 'block';
        } else {
          descendents[i].style.display = 'none';
        }
      }
    }
  }
</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r, echo=FALSE, message=F, warning=F, results = 'hide'}
library(leaflet)
library(leaflet.extras)
library(leaflet.minicharts)
library(rgdal)
library(RCurl)
library(XML)
library(tidyverse)
library(ggmap)
library(raster)
library(sp)
library(htmltools)
library(htmlwidgets)
library(legendreverse)
library(data.table)

round_percent <- function(x) { 
  if(!any(is.na(x))) {
    x <- x/sum(x)*100  # Standardize result
    res <- floor(x)    # Find integer bits
    rsum <- sum(res)   # Find out how much we are missing
    if(rsum<100) { 
        # Distribute points based on remainders and a random tie breaker
        o <- order(x%%1, sample(length(x)), decreasing=TRUE) 
        res[o[1:(100-rsum)]] <- res[o[1:(100-rsum)]]+1
    } 
    res 
  }
}

states <- readRDS("data/IndiaAdminUnits/States_2011_simplified_1.rds")
states <- states[order(as.numeric(states$ID_1)),]
centroids <- getSpPPolygonsLabptSlots(states)
states[['Centroids']] <- centroids

url <- 'https://en.wikipedia.org/wiki/2011_Census_of_India'
url_parsed <- htmlParse(getURL(url), asText = TRUE)
tableNodes <- getNodeSet(url_parsed, '//*[@id="mw-content-text"]/div/table[6]')
populationData <- readHTMLTable(tableNodes[[1]], header=TRUE, colClasses = c("integer", rep("character",3), "FormattedInteger", "double", rep("FormattedInteger", 3), "double", rep("FormattedInteger",4), "Percent"))

setnames(populationData, old = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15), new = c("Rank", "State/UT Name", "Capitals", "Type", "Population", "% of Total Population", "Males", "Females", "Gender Ratio", "Literacy Rate (%)", "Rural Population", "Urban Population", "Area (sqkm)", "Density (per sqkm)", "Decadal Growth%(2001-2011)"))

populationData <- populationData[-36,]

populationData["Urban Rural Ratio"] <- round(populationData$`Urban Population`/populationData$`Rural Population`,2) 
populationData["Urban %"] <- round(100*populationData$`Urban Population`/populationData$Population,2)
populationData["Rural %"] <- round(100*populationData$`Rural Population`/populationData$Population,2)


populationData <- populationData[order(populationData$`State/UT Name`),]

#Add NAs for parts of Kashmir outside LOC
populationData[nrow(populationData)+1,] <- NA
populationData[36, "Area (sqkm)"] <- 123512
states@data[36, "State.Name"] <- "Outside LOC"

states@data <- cbind(states@data,  populationData[,3:18])

plotSubset <- subset(states, states$`Area (sqkm)` > 1500)

#Hover content
hoverlabelsPopD <- lapply(seq(nrow(states@data)), function(i) {
  if (is.na(states@data[i, "Population"])) {
    return(paste0('<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/>",         states@data[i, "State...UT"])))
  }
  paste0( '<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/>
        <div style='width:95%%'>
        <span style='float:left'>Population:</span>
        <span style='float:right'> %s (%s%%)</span><br/>
        <span style='float:left'>Area (sqkm):</span>
        <span style='float:right'> %s (%s%%)</span><br/>
        <span style='float:left'>Population Density:</span>
        <span style='float:right'> %s/sqkm</span>
        </div>
        </div>",
        states@data[i, "State...UT"],
        format(states@data[i, "Population"], big.mark=","),
        states@data[i, "% of Total Population"],
        format(states@data[i, "Area (sqkm)"], big.mark=","), 
        format(round(100.0*states@data[i, "Area (sqkm)"]/3287240,2)),
        states@data[i, "Density (per sqkm)"]
      ), '</p>' ) 
})

hoverlabelsPopG <- lapply(seq(nrow(states@data)), function(i) {
  if (is.na(states@data[i, "Population"])) {
    return(paste0('<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/></div>",         states@data[i, "State...UT"])))
  }
  paste0( '<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/>
        <div style='width:95%%'>
        <span style='float:left'>Population Growth:</span>
        <span style='float:right'> %s %%</span><br/>
        <span style='float:left'>Population:</span>
        <span style='float:right'> %s</span><br/>
        </div>
        </div>",
        states@data[i, "State...UT"],
        states@data[i, "Decadal Growth%(2001-2011)"],
        format(states@data[i, "Population"], big.mark=",")
      ), '</p>' ) 
})

hoverlabelsLit <- lapply(seq(nrow(states@data)), function(i) {
  if (is.na(states@data[i, "Population"])) {
    return(paste0('<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/></div>",         states@data[i, "State...UT"])))
  }
  paste0( '<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/>
        <div style='width:95%%'>
        <span style='float:left'>Literacy Rate:</span>
        <span style='float:right'> %s %%</span><br/>
        <span style='float:left'>Population:</span>
        <span style='float:right'> %s</span><br/>
        <span style='float:left'>Non-literate:</span>
        <span style='float:right'> %s</span><br/>
        </div>
        </div>",
        states@data[i, "State...UT"],
        states@data[i, "Literacy Rate (%)"],
        format(states@data[i, "Population"], big.mark=","),
        format(round((100-states@data[i, "Literacy Rate (%)"])*states@data[i, "Population"]/100.0,0), big.mark=",")
      ), '</p>' ) 
})

hoverlabelsGR <- lapply(seq(nrow(states@data)), function(i) {
  if (is.na(states@data[i, "Males"]) || is.na(states@data[i, "Females"])) {
    return(paste0('<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/></div>",         states@data[i, "State...UT"])))
  }
  nums <- round_percent(c(100*states@data[i, "Males"]/states@data[i, "Population"],100*states@data[i, "Females"]/states@data[i, "Population"]))
  paste0( '<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/>
        Gender Ratio: %s<br/>
        <div style='width:95%%'>
        <span style='float:left'>Males</span>
        <span style='float:right'>Females</span>
        <br/>
        <span style='color:#2aa1ec;float:left'>%s%%</span>
        <span style='color:#fe6a59;float:right'>%s%%</span><br clear='all'/>
        <span style='background:#2aa1ec;width:%s%%;float:left'>&nbsp;</span>
        <span style='background:#fe6a59;width:%s%%;float:right'>&nbsp;</span>
        <span style='float:left'>Males: </span>
        <span style='float:right'>%s</span><br clear='all'/>
        <span style='float:left'>Females: </span>
        <span style='float:right'>%s</span><br/>
        <span style='float:left'>Difference: </span>
        <span style='float:right'>%s</span>
        </div>
        </div>",
        states@data[i, "State...UT"],
        states@data[i, "Gender Ratio"],
        nums[1], nums[2],
        nums[1], nums[2],
        format(states@data[i, "Males"], big.mark=","), format(states@data[i, "Females"], big.mark=","), format(states@data[i, "Males"] - states@data[i, "Females"], big.mark=",")
      ), '</p>' ) 
})

hoverlabelsUR <- lapply(seq(nrow(states@data)), function(i) {
  if (is.na(states@data[i, "Urban Population"]) || is.na(states@data[i, "Rural Population"])) {
    return(paste0('<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/></div>",         states@data[i, "State...UT"])))
  }
  nums <- round_percent(c(as.numeric(states@data[i, "Urban %"]),as.numeric(states@data[i, "Rural %"])))
  paste0( '<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/>
        Urban:Rural Ratio: %s<br/>
        <div style='width:95%%'>
        <span style='float:left'>Urban</span>
        <span style='float:right'>Rural</span>
        <br/>
        <span style='color:#2aa1ec;float:left'>%s%%</span>
        <span style='color:#fe6a59;float:right'>%s%%</span><br clear='all'/>
        <span style='background:#2aa1ec;width:%s%%;float:left'>&nbsp;</span>
        <span style='background:#fe6a59;width:%s%%;float:right'>&nbsp;</span>
        <span style='float:left'>Urban Population: </span>
        <span style='float:right'>%s</span><br/>
        <span style='float:left'>Rural Population: </span>
        <span style='float:right'>%s</span><br/>
        <span style='float:left'>Total Population: </span>
        <span style='float:right'>%s</span>
        </div>
        </div>",
        states@data[i, "State...UT"],
        states@data[i, "Urban Rural Ratio"],
        nums[1],nums[2],
        nums[1],nums[2],
        format(states@data[i, "Urban Population"], big.mark=","), format(states@data[i, "Rural Population"], big.mark=","), format(states@data[i, "Population"], big.mark=",")
      ), '</p>' ) 
})

```

## {.tabset}
### Population Density^[1]^

<div class = "col-md-8">
<div class = "row">
```{r, echo=FALSE, warning=F}
mapspalettePopD <- colorNumeric(
  palette = "YlOrRd",
  domain = plotSubset$`Density (per sqkm)`
)

mapspalettePOPG <- colorNumeric(
  palette = "YlOrRd",
  domain = plotSubset$`Decadal Growth%(2001-2011)`
)

mapspaletteLit <- colorNumeric(
  palette = "Blues",
  domain = plotSubset$`Literacy Rate (%)`
)

mapspaletteGR <- colorNumeric(
  palette = "YlOrRd",
  reverse = T,
  domain = plotSubset$`Gender Ratio`
)

mapspaletteUR <- colorNumeric(
  palette = "YlOrRd",
  reverse = T,
  domain = as.numeric(plotSubset@data$`Urban Rural Ratio`)
)

map <- leaflet(width = "100%") %>% 
  addProviderTiles("Esri") %>%
  leafem::addMouseCoordinates() %>% 
  
  addPolygons(data = states,
              color = "#000000", 
              weight = 1, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.8,
              dashArray = "3",
              fillColor = ~mapspalettePopD(states$`Density (per sqkm)`),
              label = lapply(hoverlabelsPopD, htmltools::HTML),
              highlightOptions = highlightOptions(color = "white", weight = 2),
              group = "Population Density (/sqkm)") %>%
  
  addPolygons(data = states,
              color = "#000000", 
              weight = 1, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.8,
              dashArray = "3",
              fillColor = ~mapspalettePOPG(states$`Decadal Growth%(2001-2011)`),
              label = lapply(hoverlabelsPopG, htmltools::HTML),
              highlightOptions = highlightOptions(color = "white", weight = 2),
              group = "Population Growth %") %>%
  
  addPolygons(data = states,
              color = "#000000", 
              weight = 1, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.8,
              dashArray = "3",
              fillColor = ~mapspaletteLit(states$`Literacy Rate (%)`),
              label = lapply(hoverlabelsLit, htmltools::HTML),
              highlightOptions = highlightOptions(color = "white", weight = 2),
              group = "Literacy Rate %") %>%
  
  addPolygons(data = states,
              color = "#000000", 
              weight = 1, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.8,
              dashArray = "3",
              fillColor = ~mapspaletteGR(as.numeric(states$`Gender Ratio`)),
              label = lapply(hoverlabelsGR, htmltools::HTML),
              highlightOptions = highlightOptions(color = "white", weight = 2),
              group = "Gender Ratio") %>%
  
  addPolygons(
    data = states,
    color = "#000000", 
    weight = 1, smoothFactor = 0.5,
    opacity = 1.0, fillOpacity = 0.8,
    dashArray = "3",
    fillColor = ~mapspaletteUR(as.numeric(states$`Urban Rural Ratio`)),
    label = lapply(hoverlabelsUR, htmltools::HTML),
    highlightOptions = highlightOptions(color = "white", weight = 2),
              group = "Urban:Rural") %>%
  
  addMiniMap(tiles = providers$Esri, toggleDisplay = T) %>% 
  addScaleBar() %>%
  addSimpleGraticule(showOriginLabel = T) %>%
  addLegend("bottomleft", pal = mapspalettePopD, values = plotSubset$`Density (per sqkm)`, title = "Population Density (/sqkm)", opacity = 1) %>%
  addLegend("bottomleft", pal = mapspalettePOPG, values = plotSubset$`Decadal Growth%(2001-2011)`, title = "Population Growth %", opacity = 1) %>%
  legendreverse("bottomleft", pal = mapspaletteLit, values = plotSubset$`Literacy Rate (%)`, title = "Literacy Rate %", opacity = 1, decreasing = T) %>% 
  legendreverse("bottomleft", pal = mapspaletteGR, values = plotSubset$`Gender Ratio`, opacity = 1, decreasing = T, title = "Gender Ratio") %>%
  legendreverse("bottomleft", pal = mapspaletteUR, values = as.numeric(plotSubset$`Urban Rural Ratio`), decreasing = T, opacity = 1, title = "Urban:Rural") %>%

htmlwidgets::onRender("
    function(el, x) {
      var myMap = this;
      myMap.on('baselayerchange',
        function (e) {
          document.getElementById('countryInfo').innerHTML = lookupCountryInfo(e.name);
          descendents = document.getElementsByClassName('leaflet-control')
          for(var i=0; i<descendents.length; i++) {
            if(descendents[i].className == 'info legend leaflet-control') {
              if (descendents[i].innerHTML.indexOf(e.name) != -1) {
                descendents[i].style.display = 'block';
              } else {
                descendents[i].style.display = 'none';
              }
            }
          }
        })

      myMap.on('tooltipopen',
        function (e) {
          document.getElementById('stateInfo').innerHTML = e.tooltip._content;
          $('.leaflet-tooltip').css('display','none');
        })

      myMap.on('tooltipclose',
        function (e) {
          document.getElementById('stateInfo').innerHTML = '';
        })
    }") %>% 
  
  addLayersControl(
    baseGroups = c("Population Density (/sqkm)", "Population Growth %", "Literacy Rate %", "Gender Ratio", "Urban:Rural"),
    options = layersControlOptions(collapsed = FALSE)
  )



  # leafem::addHomeButton(ext = bbox([]))

  css_fix <- "div.info.legend.leaflet-control br {clear: both;}"
  map <- map %>% prependContent(tags$style(type = "text/css", css_fix))  

  map
  
```
<font size="1">*2011 Census and State/UT boundaries<br/>
Source: <br/>
[1]https://en.wikipedia.org/wiki/Demographics_of_India<br/>
[2]https://en.wikipedia.org/wiki/Geography_of_India
</font>
</div>
</div>
<div class = "col-md-3">
<div class = "row"  style = "margin-left: 10px">
<h2><b>India</b></h2></br>
<div id = "countryInfo">
</div><br>
<div id = "stateInfo">
</div>
</div>
</div>

### Data^[1]^

```{r}
library(DT)
populationData <- populationData[order(populationData$Rank),]
populationData <- populationData[-36,]
col2cnvrt <- c(1, 5:18)
col2cnvrt2 <- c(0, 4:17) #because !#$@# columnDefs indexes from 0
populationData[,col2cnvrt] <- lapply(populationData[,col2cnvrt],function(x){format(round(as.numeric(x), 2), big.mark=",")})
datatable(populationData, rownames = FALSE, options = list(pageLength = 35, columnDefs = list(list(className = 'dt-right', targets = col2cnvrt2))))
```
<font size="1">
Source: 
[1]https://en.wikipedia.org/wiki/Demographics_of_India</font>

### Info
```{r}
sessionInfo()
```