---
output: html_document
---

<style>
    body .main-container {
        max-width: 100%;
        padding: 0;
        margin: 0;
    }
</style>

<script>
  function lookupCountryInfo(val) {
    var result = "";

    var lookup = {
      "High Quality": "<p></p>",
      
      "Medium Quality": "<p></p>",
      
      "Legal Enforcement": "<p></p>",
      
      "Social Acceptance": "<p></p>"
    };
  
    result = lookup[val];
  
    return result;
  }

  window.onload = function () {
    document.getElementById("countryInfo").innerHTML = lookupCountryInfo("High Quality");
    descendents = document.getElementsByClassName('leaflet-control');
    for(var i=0; i<descendents.length; i++) {
      if(descendents[i].className == 'info legend leaflet-control') {
        if (descendents[i].innerHTML.indexOf("High Quality") != -1) {
          descendents[i].style.display = 'block';
        } else {
          descendents[i].style.display = 'none';
        }
      }
    }
  }
</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r, echo=FALSE, message=F, warning=F, results = 'hide'}
library(leaflet)
library(leaflet.extras)
library(leaflet.minicharts)
library(rgdal)
library(RCurl)
library(XML)
library(tidyverse)
library(ggmap)
library(raster)
library(sp)
library(htmltools)
library(htmlwidgets)
library(legendreverse)
library(data.table)
library(rvest)

states <- readRDS("data/IndiaAdminUnits/States_2011_simplified_1.rds")
states <- states[order(as.numeric(states$ID_1)),]
centroids <- getSpPPolygonsLabptSlots(states)
states[['Centroids']] <- centroids

dat <- read.csv("data/weed/StateNames.txt", header = F)
#print(data)


#Specifying the url for desired website to be scraped
baseurl <- 'http://www.priceofweed.com/prices/India/'

get_page_data <- function(url) {
  print(url)
  medQAv <- url
  tryCatch({
    medQAv <- xml2::read_html(medQAv) %>%
      html_nodes(xpath='//*[@id="contentdt"]/table[1]') %>%
      html_table(fill = T)
    
    hiVals <- medQAv[[1]]$X2[2]
    medVals <- medQAv[[1]]$X2[3]
    
    return(c(hiVals,medVals))
    
  }, warning = function(w) {
    return(c(NA,NA))
  }, error = function(e) {
    return(c(NA,NA))
  }
  )
}

vals <- c()

for(i in dat$V1){
  #Reading the HTML code from the website
  url <- paste0(baseurl,i,".html")
  vals <- rbind(vals,get_page_data(url))
}

valsbak <- vals
vals[,] <- gsub("\\$","",vals[,])
vals[,] <- gsub("N\\/A","NA",vals[,])

vals <- cbind(as.numeric(vals[,1]), as.numeric(vals[,2]))
# vals <- c(NA,232.77,NA,3.40,240.00,36.05,106.39,800.00,NA,239.80,77.65,317.22,385.57,102.08,100.00,NA,175.19,144.57,NA,20.00,398.31,NA,NA,352.27,852.27,28571.43,NA,308.14,NA,NA,179.79,NA,153.75,222.05,312.29,NA)
# vals <- cbind(vals,c(115.00,106.89,NA,54.45,142.05,156.02,NA,284.09,NA,237.95,100.33,204.92,134.01,120.00,NA,2.25,144.66,81.33,NA,116.71,150.60,1428.57,285.71,2130.68,NA,4.50,56.82,446.17,NA,NA,176.05,NA,136.29,8.50,84.03,NA))
LE <- c(NA,3,NA,2,1,4,5,3,NA,3,3,3,3,4,3,2,3,4,NA,2,3,4,5,1,NA,4,NA,4,NA,NA,3,NA,3,2,3,NA)
SA <- c(NA,3,NA,3,4,2,1,3,NA,3,3,3,3,3,2,4,3,2,NA,3,3,1,3,2,NA,2,NA,2,NA,NA,2,NA,3,2,3,NA)

colnames(vals) <- c("High Quality","Medium Quality")

states[["High Quality"]] <- as.numeric(vals[,1])
states[["Medium Quality"]] <- as.numeric(vals[,2])
states[["Legal Enforcement"]] <- as.numeric(LE)
states[["Social Acceptance"]] <- as.numeric(SA)

#states@data <- cbind(states@data,  vals[,])

plotSubset <- subset(states, states$`High Quality` < 5000)


#Hover content
hoverlabelsPopD <- lapply(seq(nrow(states@data)), function(i) {
  if (is.na(states@data[i, "High Quality"])) {
    return(paste0('<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/>",states@data[i, "State...UT"])))
  }
  paste0( '<p>', sprintf(
        "<div style='font-size:12px;width:200px;float:left'>
        <hr><span style='font-size:12px;font-weight:bold'>%s</span><br/>
        <div style='width:95%%'>
        <span style='float:left'>High Quality:</span>
        <span style='float:right'> %s</span><br/>
        <span style='float:left'>Medium Quality:</span>
        <span style='float:right'> %s</span><br/>
        <span style='float:left'>Legal Enforcement (on a scale of 5):</span>
        <span style='float:right'> %s</span><br/>
        <span style='float:left'>Social Acceptance (on a scale of 5):</span>
        <span style='float:right'> %s</span>
        </div>
        </div>",
        states@data[i, "State...UT"],
        states@data[i, "High Quality"],
        states@data[i, "Medium Quality"],
        states@data[i, "Legal Enforcement"], 
        states@data[i, "Social Acceptance"]
      ), '</p>' ) 
})


```

## {.tabset}
### Price of Weed^[1]^

<div class = "col-md-8">
<div class = "row">
```{r, echo=FALSE, warning=F}
mapspalettePopD <- colorQuantile(
  palette = "YlOrRd",
  domain = states@data$`High Quality`, n = 7, right = TRUE
)

mapspalettePOPG <- colorQuantile(
  palette = "YlOrRd",
  domain = states@data$`Medium Quality`, n = 7, right = TRUE
)

mapspaletteLE <- colorNumeric(
  palette = "YlOrRd",
  na.color = "#808080",
  domain = c(NA,1,2,3,4,5)
)

mapspaletteSA <- colorNumeric(
  palette = "YlOrRd",
  na.color = "#808080",
  domain = c(NA,1,2,3,4,5)
)

map <- leaflet(width = "100%") %>% 
  addProviderTiles("Esri") %>%
  leafem::addMouseCoordinates() %>% 
  
  addPolygons(data = states,
              color = "#000000", 
              weight = 1, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.8,
              dashArray = "3",
              fillColor = ~mapspalettePopD(states$`High Quality`),
              label = lapply(hoverlabelsPopD, htmltools::HTML),
              highlightOptions = highlightOptions(color = "white", weight = 2),
              group = "High Quality") %>%
  
  addPolygons(data = states,
              color = "#000000", 
              weight = 1, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.8,
              dashArray = "3",
              fillColor = ~mapspalettePOPG(states$`Medium Quality`),
              label = lapply(hoverlabelsPopD, htmltools::HTML),
              highlightOptions = highlightOptions(color = "white", weight = 2),
              group = "Medium Quality") %>%
  
  addPolygons(data = states,
              color = "#000000", 
              weight = 1, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.8,
              dashArray = "3",
              fillColor = ~mapspaletteLE(states$`Legal Enforcement`),
              label = lapply(hoverlabelsPopD, htmltools::HTML),
              highlightOptions = highlightOptions(color = "white", weight = 2),
              group = "Legal Enforcement") %>%
  
  addPolygons(data = states,
              color = "#000000", 
              weight = 1, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.8,
              dashArray = "3",
              fillColor = ~mapspaletteSA(states$`Social Acceptance`),
              label = lapply(hoverlabelsPopD, htmltools::HTML),
              highlightOptions = highlightOptions(color = "white", weight = 2),
              group = "Social Acceptance") %>%
  
  addMiniMap(tiles = providers$Esri, toggleDisplay = T) %>% 
  addScaleBar() %>%
  addSimpleGraticule(showOriginLabel = T) %>%
  addResetMapButton() %>%
  addSearchOSM(options = search) %>%
  addFullscreenControl() %>% 
  addLegend("bottomleft", pal = mapspalettePopD, values = states$`High Quality`, title = "High Quality", opacity = 1, labFormat = function(type, cuts, p) {
  n = length(cuts)
  p = paste0(round(p * 100), '%')
  cuts = paste0(round(cuts[-1],0))}) %>%
  addLegend("bottomleft", pal = mapspalettePOPG, values = states$`Medium Quality`, title = "Medium Quality", opacity = 1, labFormat = function(type, cuts, p) {
  n = length(cuts)
  p = paste0(round(p * 100), '%')
  cuts = paste0(round(cuts[-1],0))}) %>%
  addLegend("bottomleft", pal = mapspaletteLE, values = c(NA, 1,2,3,4,5), title = "Legal Enforcement", opacity = 1, bins =5) %>%
  addLegend("bottomleft", pal = mapspaletteSA, values = c(NA, 1,2,3,4,5), title = "Social Acceptance", opacity = 1, bins = 5) %>%
  
htmlwidgets::onRender("
    function(el, x) {
      var myMap = this;
      myMap.on('baselayerchange',
        function (e) {
          document.getElementById('countryInfo').innerHTML = lookupCountryInfo(e.name);
          descendents = document.getElementsByClassName('leaflet-control')
          for(var i=0; i<descendents.length; i++) {
            if(descendents[i].className == 'info legend leaflet-control') {
              if (descendents[i].innerHTML.indexOf(e.name) != -1) {
                descendents[i].style.display = 'block';
              } else {
                descendents[i].style.display = 'none';
              }
            }
          }
        })

      myMap.on('tooltipopen',
        function (e) {
          document.getElementById('stateInfo').innerHTML = e.tooltip._content;
          $('.leaflet-tooltip').css('display','none');
        })

      myMap.on('tooltipclose',
        function (e) {
          document.getElementById('stateInfo').innerHTML = '';
        })
    }") %>% 
  
  addLayersControl(
    baseGroups = c("High Quality", "Medium Quality", "Legal Enforcement", "Social Acceptance"),
    options = layersControlOptions(collapsed = F)
  )



  # leafem::addHomeButton(ext = bbox([]))

  css_fix <- "div.info.legend.leaflet-control br {clear: both;}"
  map <- map %>% prependContent(tags$style(type = "text/css", css_fix))  

  map
  
```
<font size="1">*2011 Census and State/UT boundaries<br/>
Source: <br/>
[1]https://www.priceofweed.com<br/>
</font>
</div>
</div>
<div class = "col-md-3">
<div class = "row"  style = "margin-left: 10px">
<h2><b>India</b></h2></br>
<div id = "countryInfo">
</div><br>
<div id = "stateInfo">
</div>
</div>
</div>

### Data^[1]^

```{r}
library(DT)

```
<font size="1">
Source: 
[1]https://www.priceofweed.com</font>

### Info
```{r}
sessionInfo()
```